---
title: "CTU Berns R Package universe"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

R package universes are similar a bit like mini-CRANs. 'The system automatically tracks registered git repositories containing R packages, builds binaries for Windows and MacOS, renders vignettes, and makes all data available through dashboards, feeds and APIs on personal subdomains'. [See here for further details of universes](https://ropensci.org/blog/2021/06/22/setup-runiverse/)

Briefly, packages should be added to [packages.json](packages.json). They are then tracked on [r-universe](https://github.com/r-universe/ctu-bern) and built each hour. A dashboard of the included packages and build status can be found [here](https://ctu-bern.r-universe.dev/ui#builds). All vignettes are also accessible via the [articles button](https://ctu-bern.r-universe.dev/ui#articles).

To use the universe, in R, do the following, which adds the universe to your list of repos (when installing packages, R will cycle through the repos until it finds the appropriate package)...

```{r, eval = FALSE}
options(repos = c(CTU = "https://ctu-bern.r-universe.dev",
        CRAN = "https://cran.rstudio.com/"))
```

It is then possible to install universe packages as if they were CRAN packages...

```{r, eval = FALSE}
install.packages("accrualPlot")
```



## Packages in the universe

```{r , echo = FALSE}

library(jsonlite)
pkgs <- sort(jsonlite::fromJSON("https://ctu-bern.r-universe.dev/packages/"))

```

```{r pressure, echo=FALSE, results='asis'}
knitr::kable(do.call("rbind", lapply(pkgs, function(x) {
  data.frame(package = x, status = glue::glue("![](https://ctu-bern.r-universe.dev/badges/{x})"))
  })))
```


